Figures

### 2018-11-02 code/figures.rmd
Updated project name in header in code files
Changed R2 to r and added bootstrap CI

---
title: "Figures"
author: "Anton Ohlsson Collentine"
output: pdf_document
---

@@

```{r load packages, data and source helper functions}
if(!require(readr)){install.packages("readr")}
if(!require(metafor)){install.packages("metafor")}
if(!require(dplyr)){install.packages("dplyr")}
if(!require(purrr)){install.packages("purrr")}
if(!require(ggplot2)){install.packages("ggplot2")}
if(!require(cowplot)){install.packages("cowplot")}

library(readr) #To load data
library(dplyr) #For data transformation
library(purrr) #For data iteration
library(metafor) #To run meta-analyses
library(ggplot2) #Plot data
library(cowplot) #Combine several plots into one

@@

@@

# summary(lm(I2 ~ z, data = res2)) #b = 69.40, R2 = 0.61

I2 <- ggplot(res2, aes(x = z, y = I2)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  xlab("Fisher's z") +
  coord_cartesian(ylim = c(0, 100)) +
  geom_text(x = 0.15, y = 80, label = "b = 69.40, R2 = 0.61", size = 3.5) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(I^2," index", sep = ""))) +
  scale_x_continuous(name = "Effect size (Fisher's z)")

# summary(lm(H2 ~ z, data = res2)) #b = 3.81, R2 = 0.53

H2 <- ggplot(res2, aes(x = z, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  xlab("Fisher's z") +
  geom_text(x = 0.14, y = 5.9, label = "b = 3.81, R2 = 0.53", size = 3.5) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(H^2," index", sep = ""))) +
  scale_x_continuous(name = "Effect size (Fisher's z)")

effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("A", "B"), align = "v") #combine plots
effect_het
# save_plot("../figures/effect-het.png", effect_het,
          # nrow = 2, base_aspect_ratio = 1.3, dpi = 600)

```{r robustness, results="hide"}
##Excluding anchoring effects
dropped_anchoring <- res2 %>%
  filter(!grepl("Anchoring", effect))

summary(lm(I2 ~ z, data = dropped_anchoring))
#b = 87.87, R2 = .51

>>>>

---
title: "Figures"
author: "Heterogeneity in direct replications in psychology and its association with effect size"
output: pdf_document
---

@@

```{r load packages, data and source helper functions}
if(!require(readr)){install.packages("readr")}
if(!require(metafor)){install.packages("metafor")}
if(!require(dplyr)){install.packages("dplyr")}
if(!require(purrr)){install.packages("purrr")}
if(!require(ggplot2)){install.packages("ggplot2")}
if(!require(cowplot)){install.packages("cowplot")}
if(!require(boot)){install.packages("boot")}

library(readr) #To load data
library(dplyr) #For data transformation
library(purrr) #For data iteration
library(metafor) #To run meta-analyses
library(ggplot2) #Plot data
library(cowplot) #Combine several plots into one
library(boot) #Bootstrap confidence intervals for correlations

@@

```{r cor_het_z}
#Basic correlations
cor.test(res2$I2, res2$z) #pearson

I2_fit <- summary(lm(I2 ~ z, data = res2))

cor.test(res2$H2, res2$z) #pearson

H2_fit <- summary(lm(H2 ~ z, data = res2))

cor.test(res2$I2, res2$z, method = "spearman") #spearman

##Excluding anchoring effects
dropped_anchoring <- res2 %>%
  filter(!grepl("Anchoring", effect))

cor.test(dropped_anchoring$I2, dropped_anchoring$z) #pearson

#bootstrap confidence intervals
#code by Amir Abdol

#I2
pear <- function(formula, data, indices){ #pearson
     d <- data[indices,]
     fit <- cor.test(formula = ~ I2 + z, data=d)
     return(fit$estimate)
}

bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ z + I2)

I2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)

spear <- function(formula, data, indices){ #spearman
     d <- data[indices,]
     fit <- cor.test(formula = ~ I2 + z, data=d, method = "spearman")
     return(fit$estimate)
}

options(warn=-1)
bootfit <- boot(data=res2, statistic=spear, R=1000, formula= ~ z + I2)
options(warn=0)

I2_ci_spear <- boot.ci(bootfit, type=c("perc", "bca"))

#Excluding anchoring effects
bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ z + I2)

I2_dropped_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)

#H2
pear <- function(formula, data, indices){
     d <- data[indices,]
     fit <- cor.test(formula = ~ H2 + z, data=d)
     return(fit$estimate)
}

bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ z + H2)

H2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))

@@

I2 <- ggplot(res2, aes(x = z, y = I2)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  xlab("Fisher's z") +
  coord_cartesian(ylim = c(0, 100)) +
  geom_text(x = 0.15, y = 80, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(italic(I)^2," index"))) +
  scale_x_continuous(name = expression(paste("Effect size (Fisher's ", italic(z), ")")))

H2 <- ggplot(res2, aes(x = z, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  xlab("Fisher's z") +
  geom_text(x = 0.14, y = 5.9, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(italic(H)^2," index", sep = ""))) +
  scale_x_continuous(name = expression(paste("Effect size (Fisher's ", italic(z),")")))

effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("A", "B"), align = "v") #combine plots
effect_het
save_plot("../figures/effect-het.png", effect_het,
          nrow = 2, base_height = 5, base_width = 5, dpi = 600)
